### 2017-05-03 paper/evaluation.tex
minor fixes

To answer this research question, we conducted an experiment involving
the six parallel levels from Section~\ref{sec:modes}  and the top 10
projects with long-running tests suites from our sample set. We are
interested in understanding how efficiency (\ie, testing cost) and
flakiness (\ie, failing tests) are affected when we run a test suite
with different parallel levels. \Jbc{I think we must have a sentence
to motivate why we want to understand this relationship}.  We used as
a \emph{control group} (\ie, baseline) the sequential execution of
each subject's tests. Notice that for measuring flakiness, we have to
consider only tests that failed due to the concurrency in the parallel
execution. To this purpose, we re-executed the tests in sequence ten
times and carefully verified that there are only passing tests in our
baseline. We considered ten as the number of re-executions based on
the approach used by Google reported in a previous work on test
flakiness~\cite{luo-etal-fse2014}. For the parallelism configurations,
we implemented a script that takes a subject and a configuration
(\eg, \ForkSeq{}) as inputs, and the script outputs the modified
version of the subject with the desired configuration. The workflow
consists in copying the project directory to a new directory, finding
all existing build files (\ie, \pomf{} files), and modifying all
existing Maven Surefire configurations with new values for the
parameters \CodeIn{parallel}, \CodeIn{forkCount}, and
\CodeIn{threadCount} using an XPath~\cite{xpath} library to manipulate
XML documents. For configurations with forked JVMs enabled (\ie,
\ForkSeq{} and \ForkParMeth{}), we changed the \CodeIn{forkCount} with
the value \CodeIn{1C} (\ie, one JVM per core). To adjust the pool of
threads for parallelism within a JVM, we changed the parameter
\CodeIn{threadCount} with \Jbc{should we consider 2 as it is the
number of native threads per core OR 6 as it represents 3 Cores * 2
native threads?}.  To run the subjects and their respective variations
(\ie, the modified versions according to the parallelism
configuration), we used a similar approach as in
Figure~\ref{fig:mvn-execution} except that we added a timeout of one
hour to run the tests. We used the \CodeIn{timeout}
command~\cite{timeout-cmd} to monitor the execution, and we configured
the command to dispatch a \emph{kill} signal if the test execution
exceeds the time limit. We imposed this time constraint to avoid
hanging indefinitely the experiment execution due to some thread
contention that may occur (\eg, deadlock). Finally, we saved each
execution log and XML test reports generated by Maven to collect the
execution time, the number of failing tests, and for reference to
analyze and diagnose outliers in our results. For efficiency, we
reported the speedup (\ie, $T_{\text{sequence}} /
T_{\text{parallel}}$) in average, and for flakiness, we reported the
rate of failing tests (\ie, $failures / tests$) in average.
Figure~\ref{tab:rq6-table} (ordered by time cost) summarizes the
obtained results.

@@

%% Table header macros
\newcommand{\subcolA}{$\Uparrow_\text{speed}$}
\newcommand{\subcolB}{$\%_\text{fail}$}
\newcommand{\colheader}[1]{\multicolumn{2}{c|}{\emph{#1}}}
\newcommand{\subcol}{\subcolA{} & \subcolB{}}
\newcommand{\entry}[2]{#1x & #2\%}

\begin{figure*}[t]
\centering
\begin{tabular}{|l|r|rr|rr|rr|rr|rr|}
\hline%

\multirow{2}{*}{\emph{Subject}} & \emph{\Seq{}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ \cline{2-12}
    & $T_\text{cost}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%

\hline%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%
Subject A & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%

@@

\hline%
\end{tabular}
\caption{\Fix{Tabela de eficiencia e flakiness}}
\label{tab:rq6-table}
\end{figure*}

>>>>

To answer this research question, we conducted an experiment involving
the six parallel configurations from Section~\ref{sec:modes}  and the
top 10 projects with long-running tests suites from our sample set. We
are interested in understanding how efficiency (\ie, testing cost) and
flakiness (\ie, failing tests) are affected when we run a test suite
with different parallel configurations. \Jbc{I think we must have a
sentence to motivate why we want to understand this relationship}.  We
used as a \emph{control group} (\ie, baseline) the sequential
execution of each subject's tests. Notice that for measuring
flakiness, we have to consider only tests that failed due to the
concurrency in the parallel execution. To this purpose, we re-executed
the tests in sequence ten times and carefully verified that there are
only passing tests in our baseline. We considered ten as the number of
re-executions based on the approach used by Google reported in a
previous work on test flakiness~\cite{luo-etal-fse2014}. For the
parallelism configurations, we implemented a script that takes a
subject and a configuration (\eg, \ForkSeq{}) as inputs, and the
script outputs the modified version of the subject with the desired
configuration. The workflow consists in copying the project directory
to a new directory, finding all existing build files (\ie, \pomf{}
files), and modifying all existing Maven Surefire configurations with
new values for the parameters \CodeIn{parallel}, \CodeIn{forkCount},
and \CodeIn{threadCount} using an XPath~\cite{xpath} library to
manipulate XML documents. For configurations with forked JVMs enabled
(\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
\CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per core).
To adjust the pool of threads for parallelism within a JVM, we changed
the parameter \CodeIn{threadCount} with \Jbc{should we consider 2 as
it is the number of native threads per core OR 6 as it represents 3
Cores * 2 native threads?}.  To run the subjects and their respective
variations (\ie, the modified versions according to the parallelism
configuration), we used a similar approach as in
Figure~\ref{fig:mvn-execution} except that we added a timeout of one
hour to run the tests. We used the \CodeIn{timeout}
command~\cite{timeout-cmd} to monitor the execution, and we configured
the command to dispatch a \emph{kill} signal if the test execution
exceeds the time limit. We imposed this time constraint to avoid
hanging indefinitely the experiment execution due to some thread
contention that may occur (\eg, deadlock). Finally, we saved each
execution log and XML test reports generated by Maven to collect the
execution time, the number of failing tests, and for reference to
analyze and diagnose outliers in our results. For efficiency, we
reported the speedup (\ie, $T_{\text{s}} / T_{\text{p}}$) in average,
and for flakiness, we reported the rate of failing tests (\ie,
$\mathit{\%_\text{fail} = failures / tests}$) in average.
Figure~\ref{tab:rq6-table} summarizes the obtained results ordered by
the time cost (\ie, $T_\text{cost}$).

@@

%% Table header macros
\newcommand{\subcolA}{$\Uparrow_\text{speed}$}
\newcommand{\subcolB}{$\%_\text{fail}$}
\newcommand{\colheader}[1]{\multicolumn{2}{c}{\emph{#1}}}
\newcommand{\subcol}{\subcolA{} & \subcolB{}}
\newcommand{\entry}[2]{#1x & #2\%}

\begin{figure*}[t]
\centering
\small
\begin{tabular}{lccccccccccc}
\toprule
\multirow{2}{*}{\emph{Subject}} & \emph{\Seq{}} &
    \colheader{\SeqClassParMeth} & \colheader{\ParClassSeqMeth} &
    \colheader{\ParClassParMeth} & \colheader{\ForkSeq} &
    \colheader{\ForkParMeth} \\ %\cline{2-12}
    & $T_\text{cost}$ & \subcol{} & \subcol{} & \subcol{} & \subcol{}
    & \subcol{}\\%
\midrule%
Choco Solver & Xm & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B} & \entry{A}{B}\\%

@@

\bottomrule%
\end{tabular}
\caption{\Fix{Tabela de eficiencia e flakiness}}
\label{tab:rq6-table}
\end{figure*}
